%% BEGIN changes.tex
%%
%% Changes listing for PSTricks.
%% Run with LaTeX, with or without the NFSS.
%%
%% Change these for a4 paper:
\def\paperwidth{8.5in}
\def\paperheight{11in}

\def\FileVersion{0.94-Beta}
\def\FileDate{April 16, 1993}

\documentstyle[12pt,fancybox]{article}

%% PAGE PARAMETERS

% Paragraphs are marked by large space rather than indentation:
\parindent 0pt
\parskip 6pt plus 1pt minus 1pt

% No headers, 1in top margin
\topmargin 0pt
\headheight 0pt
\headsep 0pt

% Total bottom margin 1in, text height 9in
\textheight 9in
\footskip .625in

% Now adjust for different paper size:
\newdimen\mydim
\mydim=\paperwidth
\advance\mydim-8.5in
\divide\mydim 2
\advance\oddsidemargin \mydim
\advance\evensidemargin \mydim
\mydim=\paperheight
\advance\mydim-11in
\divide\mydim 2
\advance\topmargin \mydim

%% OTHER

\renewcommand{\EveryVerbatimLine}[2]{}

% Short meta (works in verbatim. Can't use < for other purposes.
\catcode`\<=13 \def<#1>{{\rm\it #1\/}}    % <meta> (works in verbatim)

% Short verbatim.
\catcode`\"=13
\def"{\verb"}

\catcode`\@=12  % In case I'm using AmS-LaTeX

\begin{document}

\begin{center}
{\large\bf Changes listing for PSTricks}\\[6pt]
  Version \FileVersion\\
  \FileDate\\[6pt]
  Timothy Van Zandt\\
  tvz@Princeton.EDU
\end{center}

  The PSTricks package is still preliminary. The features list
  and user interface are unlikely to change much in the short term, but
  the internal code is not stable.

\section{VERSION 0.94 (Beta)}

\subsection{Incompatible changes}

  \begin{enumerate}

    \item "\Rnode" uses the graphics parameters "href" and "vref" to set the
reference point, rather than having a coordinate argument.

  \end{enumerate}

\subsection{New features}

  \begin{enumerate}

  \item New graphics objects: "\pstriangle", "\psdiamond", "\psdot".

  \item New box frames: "\pstribox", "\psdiabox".

  \item New nodes: "\dotnode", "\dianode", "trinode".

  \item Tree macros!

  \item "\psmatrix": Good for math diagrams and graphs.

  \item Negative nodesep and offset measure distance from center of node.

  \item New node connections: "\ncbox", "\ncarcbox".

  \item New node label puts: "\ncput", "\naput", "\nbput". (These replace
"\lput", "\mput", "\aput", "\Aput", "\bput" and "\Bput", which are still
supported.)

  \item New node label puts (especially good for trees): "\thput", "\tvput",
"\tlput", "\trput", "\taput", "\tbput". (Make "\ncline" obsolete, but this is
still supported.)

  \item "\nput", for attaching labels to nodes.

  \item New arrow styles: {\catcode`\<=12 "|<->|" and "|<*->|*"}.

  \item New dot styles: "diamond", "diamond*", "oplus", "ominus", "x",
"asterisk".

 \end{enumerate}

\subsection{Obsolete but supported features}

  \begin{enumerate}

  \item "\lput", "\mput", "\aput", "\Aput", "\bput" and "\Bput".

  \item "\ncline".

  \end{enumerate}
\subsection{Bug fixes}

  \begin{enumerate}

    \item Fixed "\ncangle" so that it would work properly with non-right angle
values of "angleA" and "angleB".

  \end{enumerate}


\subsection{Other changes}

  \begin{enumerate}

     \item "\OldPsput" and "\NewPsput" are back in "pstricks.tex".

     \item The <num> in "arrowsize=<dim num>", "tbarsize=<dim num>", and
"dotsize=<dim num>" is optional (default=0).

  \end{enumerate}


\end{document}
%% END changes.tex
